### 2019-02-26 report/final-report.tex
minor edit to conclusion

During the course of this project, we have designed, analyzed and implemented algorithms that demonstrate it is possible to synthesize three classes of bidirectional transformations:  (1) pure bijective transformations, (2) bijections modulo equivalences classes and (3) bijections modulo projections.  The synthesis algorithms we have designed take inputs that include a format specification (which includes specification of equivalence classes) and a collection of examples.  As the class of transformations becomes richer, the number of potential programs grows dramatically.  As a result, the corresponding inference algorithm slows and its ability to guess the transformation desired by the user decreases, leading to reduced accuracy.  We found that it was possible to overcome such challenges through new heuristics that use information theory to help guide the search for program transformations.  In addition, we found the use of compositional synthesis, which is the process of breaking down a complex synthesis task into smaller, more mangeable subtasks critical when attempting to scale our prototype system up to be able to handle larger transformation task.

>>>>

During the course of this project, we have designed, analyzed and
implemented algorithms that demonstrate it is possible to synthesize
three classes of bidirectional transformations: (1) pure bijective
transformations, (2) bijections modulo equivalences classes (quotient
lenses) and (3)
bijections modulo projections (symmetric lenses).  The synthesis algorithms we have
designed take inputs that include a format specification (which
includes specification of equivalence classes) and a collection of
examples.  As the class of transformations becomes richer, the number
of potential programs grows dramatically.  As a result, the
corresponding inference algorithm slows and its ability to guess the
transformation desired by the user decreases, leading to reduced
accuracy.  We found that it was possible to overcome such challenges
through new heuristics that use information theory to help guide the
search for program transformations.  In addition, we found the use of
compositional synthesis, which is the process of breaking down a
complex synthesis task into smaller, more mangeable subtasks critical
when attempting to scale our prototype system up to be able to handle
larger transformation task.
